---
format: html
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Demo survey of reactive plot

::: {.callout-note}
This is a demo survey showcasing the functionality of <a href="https://surveydown.org" target="_blank">surveydown</a>. It doesn't collect any data.

The GitHub repo of this demo can be accessed <a href="https://github.com/surveydown-dev/demo-reactive-plot" target="_blank">here</a>.
:::

Here is a basic "multiple choice" question. The results will be displayed on the next page, showing both the choice you made as well as a summary of all the choices made by other participants.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins',
  label = "Which type of penguin do you like the best?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo'
  )
)

sd_next()
```

:::

::: {#results .sd-page}

You chose: **`r sd_output("penguins", type = "value")`**

Summary of what everyone else has chosen:

```{r}
plotOutput('penguin_plot')
```

:::
